---
title: "optschools_publicviews.Rmd"
author: "Rebecca Johnson"
date: "12/1/2020"
output: html_document
---

## Load packages


```{r}

library(xlsx)
library(dplyr)
library(stringr)
library(haven)
library(ggplot2)
library(tidyverse)
library(data.table)
library(viridis)
library(skimr)
library(qualtRics)
library(car)

theme_new <- function(base_size = 16, base_family = "Helvetica"){
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(
      panel.grid = element_blank(),   
      panel.border = element_rect(fill = NA, colour = "black", size=1),
      panel.background = element_rect(fill = "white", colour = "black"), 
      strip.background = element_rect(fill = NA),
      axis.text.x = element_text(color = "black"),
      axis.text.y = element_text(color = "black")
    )
}


```


# Load and clean data

```{r}

# Load qualtrics data
raw_data= read_survey("../data/Beliefs about funding models _rjrevis_December 1, 2020_11.06.csv")

# Load prolific dem
prol_dem = read.csv("../data/prolific_export_5fc0ff8b87f2d307d12a6324.csv")

print(sprintf("Out of %s unique ids in prolific df, %s are found in qualtrics df",
        length(unique(prol_dem$participant_id)),
        length(intersect(unique(prol_dem$participant_id),
                     unique(raw_data$prol_id)))))

prol_notfound = setdiff(prol_dem$participant_id,
                        raw_data$prol_id)

prol_dem = prol_dem %>%
        mutate(is_notfound = ifelse(participant_id %in% prol_notfound, TRUE, FALSE),
               is_missing_completetime = ifelse(completed_date_time == "", TRUE, FALSE)) 

## see that mostof the prolific not found are missing a complete day/time
## but there's also 1 missing completedatetime who's found in qualtrics
table(prol_dem$is_notfound, prol_dem$is_missing_completetime)

## rename prolific cols to distinguish b/t qualtrics cols
colnames(prol_dem) = sprintf("%s_prolific",
                             colnames(prol_dem))



# Create flags
## from looking at labels:
### [w/m]_rankfair_1 == lottery
### [w/m]_rankfair_2 == fcfs
### [w/m]_rankfair_3 == points
### and then values within are ranking
raw_data = raw_data %>%
        mutate(is_prol_r = ifelse(grepl("^5", prol_id), 
                                  TRUE, FALSE),
               is_any_barriers = ifelse(Cond %in% c("Min", "Wom"), TRUE,
                                  FALSE),
                points_rank= case_when(
                          !is.na(w_rankfair_3) ~ w_rankfair_3,
                          !is.na(m_rankfair_3) ~ m_rankfair_3),
                lottery_rank = case_when(
                          !is.na(w_rankfair_1) ~ w_rankfair_1,
                          !is.na(m_rankfair_1) ~ m_rankfair_1),
                fcfs_rank = case_when(
                          !is.na(w_rankfair_2) ~ w_rankfair_2,
                          !is.na(m_rankfair_2) ~ m_rankfair_2),
               ## reverse code points so that same direction as binary
               points_rank_rev = 3-points_rank,
                is_points_first = case_when(points_rank == 1 ~ TRUE, 
                                        TRUE ~ FALSE)) 


## left join prolific cols onto raw data
raw_data_wp = merge(raw_data,
                    prol_dem,
                    by.x = "prol_id",
                    by.y= "participant_id_prolific",
                    all.x = TRUE)

## subset to analytic df
analytic_df = raw_data_wp %>%
          filter(is_prol_r) 

## make colnames lowercase and remove spaces/punctuation
colnames(analytic_df) = gsub("\\s+|\\(|\\)", 
                             "", 
                             tolower(colnames(analytic_df)))


## later: add coding of just-world scale



```


# Summarize descriptive stats


```{r}

# Distribution of duration across conditions
## median duration is 6 minutes
## slightly lower for the people who read about historical barriers
quantile(analytic_df$durationinseconds)
analytic_df %>%
  group_by(is_any_barriers) %>%
  summarise(quant = paste(quantile(durationinseconds),
                      collapse = "; ")) 

# Conditions
table(analytic_df$cond)

# Demographics
dem_vars = c("employment.status_prolific",
             "sex_prolific",
             "first.language_prolific")

lapply(analytic_df[, dem_vars],
       function(x) table(x)) 

## skews younger
ggplot(analytic_df, aes(x = age_prolific)) +
  geom_density() 



```

## Check free response display logics


```{r}

rank_cols = grep("\\_rank$", colnames(analytic_df),
                 value = TRUE) 
fr_cols = grep("fr\\_1$", colnames(analytic_df),
               value = TRUE)

check_logic <- function(one_fr){
  
  ## first filter to those who filled out the fr
  fill_resp = analytic_df %>%
          filter(!is.na(!!sym(one_fr)))
  
  ## then, what the first choice should be
  choices = unlist(strsplit(gsub("\\_fr\\_1", "", one_fr),
                     split = ""))
  first = choices[1]
  second = choices[2]
  
  ## make sure rank matches choices
  ### first 
  if((first == "p" & all(fill_resp$points_rank == 1)) |
     (first == "f" & all(fill_resp$fcfs_rank == 1)) |
     (first == "l" & all(fill_resp$lottery_rank == 1))){
    print(sprintf("passed first choice for: %s",
                  one_fr))
  } else{
    print(sprintf("failed first choice for: %s",
                  one_fr))
  }
  
  ### second
  if((second == "p" & all(fill_resp$points_rank == 2)) |
     (second == "f" & all(fill_resp$fcfs_rank == 2)) |
     (second == "l" & all(fill_resp$lottery_rank == 2))){
    print(sprintf("passed second choice for: %s",
                  one_fr))
  } else{
    print(sprintf("failed second choice for: %s",
                  one_fr))
  }
  return(NULL)
  
}

checking <- lapply(fr_cols, check_logic)

```

# Descriptives on outcome

```{r}
## first, show raw distribution of ranks
ggplot(analytic_df, aes(x = points_rank,
                        group = cond,
                        fill = cond)) +
  geom_histogram(bins = 3, position = "dodge") +
  theme_new() +
  scale_fill_viridis(discrete = TRUE) +
  xlab("Ranking of points system (1 = first; 3 = last)") +
  theme(legend.position = c(0.7, 0.7)) +
  labs(fill = "")

## since uneven counts between any barriers and 
## no barriers, get proportions
prop_choose = analytic_df %>%
        group_by(points_rank, is_any_barriers) %>%
        summarise(num = n()) %>%
        left_join(analytic_df %>%
                group_by(is_any_barriers) %>%
                summarise(denom = n())) %>%
        mutate(prop_choose = num/denom) %>%
        ungroup() 

ggplot(prop_choose, aes(x = points_rank,
                        y = prop_choose,
                        group = is_any_barriers,
                        fill = is_any_barriers)) +
  geom_bar(stat = "identity",
           position = "dodge") +
  theme_new() +
  scale_fill_viridis(discrete = TRUE) +
  xlab("Ranking of points system (1 = first; 3 = last)") +
  theme(legend.position = c(0.7, 0.7)) +
  labs(fill = "Any barriers info?") 




```


# Analytic

## Hyp 1: barriers tx causes (1) higher ranking of points system (lower rank) and (2) higher likelihood of ranking points first

```{r}
## continuous regressing rank of points
## reverse coded so that pos coef = rank higher
summary(lm(points_rank_rev ~ is_any_barriers,
           data = analytic_df))

## binary regressing points as first
## use lpm
summary(lm(is_points_first ~ is_any_barriers,
           data = analytic_df))


```

## Hyp 2: differences between minority and women

### One way to analyze (simpler to explain/interpret)

1. Filter to respondents randomized to those two
2. Reg is comparing those two


```{r}

## when women is the tx, slightly more likely
## to rank points higher/first than when minority is tx
summary(lm(points_rank_rev ~ cond,
           data = analytic_df %>%
             filter(cond != "No_info")))

summary(lm(is_points_first ~ cond,
           data = analytic_df %>%
             filter(cond != "No_info")))


```

### A second way to analyze (recommend less)

1. Keep all respondents
2. Create dummy indicators for women barriers (compared to neither or min),
minority barriers (compared to neither or wom)
3. Use linear hypothesis test of whether coef on female == coef on minority


```{r}
analytic_df = analytic_df %>%
          mutate(wom_binary = ifelse(cond == "Wom", TRUE, FALSE),
                 min_binary = ifelse(cond == "Min", TRUE, FALSE))  


cont_compare = lm(points_rank_rev ~ wom_binary + min_binary,
           data = analytic_df)
summary(cont_compare)
linearHypothesis(cont_compare, c("wom_binaryTRUE" = "min_binaryTRUE"))

# etc



```


## Hyp 3: interaction b/t respondent demographics and treatment

Interact condition and attribute; coef of interest is between barriers treatment
and having that demographic coefficient (eg whether barriers tx is more effective
if you're a female; similar for minority)

```{r}
## create female binary if not equal to female (so includes one data expired + male)

analytic_df = analytic_df %>%
          mutate(is_female = ifelse(sex_prolific == "Female", TRUE, 
                                    FALSE)) 

summary(lm(points_rank_rev ~ cond*is_female,
           data = analytic_df))



```



## Hyp 4: something with just world or other predictors?


# Consolidate free responses so easier to read through


```{r}

## consolidate fr into one col
fr_2_cols = grep("fr\\_2$", colnames(analytic_df),
                 value = TRUE)

```
